---
title: "ce_scraping_rmd_to_database"
output: html_document
---

```{r,echo = FALSE}
library(tidyverse)
library(dplyr)
library(plotly)
library(ggplot2)
library(httr)
library(stringr)
library(rvest)
library(xml2)  #XML package no longer maintained. xml2 is a newer wrapper
library(XML)
#library(R.utils)
library(tidyjson)
library(reticulate)
library(jsonlite)
```

# Obtain a list of file names from the .rds files
```{r}
file_list <- list.files(path = "../data/bat_page_responses/group_a/rows_1_500", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = TRUE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
```

```{r}
#file_list[2]%>%
#  str_remove_all(".rds")%>%
#  str_remove_all("(rows_\\d+_\\d+/)")

file_list
```

```{r}
sample_files <- (file_list#%>%
#                   str_remove_all(".rds")%>%
#                   str_replace_all("(rows_\\d+_\\d+/)","")
                 )%>%
  sample(10)
```

```{r}
sample_files#[1]
```
#LISTING ESSENTIALS
```{r}
request <- read_rds("../data/bat_page_responses/group_a/rows_1_500/"%>%
                      paste0(sample_files[1]))

request%>%attributes()
```
```{r}
content(request)%>%
  html_nodes(xpath ='//ul[@class="listing-essentials-items"]')%>%
  html_children()
```
```{r}
request<- read_rds("../data/bat_page_responses/group_a/rows_501_5000/rows_1_1933/10020101.rds")
```

Lot Number
```{r}
scrape_lot_number <- function(x) {
  lot_number <- x%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=1]')%>%
  html_text()%>%
  str_extract("\\d+")
  ;x 
}
```


```{r}
lot_number <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=1]')%>%
  html_text()%>%
  #str_extract("\\d+")
  parse_number()
typeof(lot_number)
lot_number
```
Seller Name
```{r}
seller_name <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=2]')%>%
  html_text()%>%
  str_remove("Seller: ")
typeof(seller_name)
seller_name
```

Seller Profile Link
```{r}
seller_profile <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=2]//a')%>%
  html_node(xpath='@href')%>%
  html_text()
typeof(seller_profile)
seller_profile
```

Location Name
```{r}
location<- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=3]')%>%
  html_text()%>%
  str_remove("Location: ")
typeof(location)
location
```

Location Google Maps Link
```{r}
location_google_maps <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=3]//a')%>%
  html_node(xpath='@href')%>%
  html_text()
typeof(location_google_maps)
location_google_maps
```

Chassis Number
```{r}
chassis <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=4]')%>%
  html_text()%>%
  str_remove("Chassis: ")
  #parse_number()
typeof(chassis)
chassis
```

Odometer
```{r}
odometer <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=5]')%>%
  html_text()%>%
  tolower()%>%
  str_remove("tmu")%>%
  str_remove("shown")
typeof(odometer)
odometer
```
TMU Indicated?
```{r}
tmu <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=5]')%>%
  html_text()%>%
  str_detect("TMU")
typeof(tmu)
tmu
```

Engine
```{r}
engine <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=6]')%>%
  html_text()
typeof(engine)
engine
```
Transmission
```{r}
transmission <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=7]')%>%
  html_text()
typeof(transmission)
transmission
```
Private Party or Dealer Listing?
```{r}
seller_type <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]//li[contains(text(),"Private Party Or Dealer") or contains(text(),"Private Party or Dealer")]')%>%
  html_text()%>%
  tolower()%>%
  str_remove("private party or dealer: ")
typeof(seller_type)
seller_type
```

Additional Dealer Charges?
```{r}
dealer_charges <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]//li[contains(text(),"Additional Charges From This Dealer: USD")]')%>%
                html_text()#%>%
 # is.na()

  #parse_number()%>%as.character()
  #str_remove("Additional Charges From This Dealer: USD ")

typeof(dealer_charges)
length(dealer_charges)
dealer_charges#%>%typeof()
dealer_charges%>%is.na()
```
Model Page
```{r}
#NEED TO IDENTIFY SYNTAX FOR SIBLING
#model_page <- 
  content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]/a')%>%
  html_nodes(xpath='@href[position()=1]')%>%
  html_text()
```

Model Tag
```{r}
model_tag <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[not(@rel)]')%>%
  html_text()%>%
  str_remove("Premium")
model_tag
```
Category Tag
```{r}
category_tag <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[@rel="category tag"]')%>%
  html_text()

category_tag
```
```{r}
#categ <- content(request)%>%
#    html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
#    html_nodes(xpath='li[@class="listing-essentials-item #listing-essentials-item-categories"]//a[@rel="category tag"]')%>%
#    html_text()
#categ  
#  if(length(category_tag)==0)
#  {
#    category_tag<-NA
#  }
#  else category_tag
#  ;category_tag

prem <- content(request)%>%html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
    html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[not(@rel)][last()]')%>%
    html_text()#%>%
#    str_detect("Premium")
prem
```

Premium Listing?
```{r}
#NEED TO IDENTIFY SYNTAX FOR SIBLING a//text()
premium <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[not(@rel)][last()]')%>%
  html_text()%>%
  str_detect("Premium")

premium
```

# AUCTION LISTING DETAILS
Vehicle description text
```{r}
vehicle_description_text <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]')%>%
  html_nodes(xpath='div/div[@class="post-excerpt"]//p[text()]')%>%
  html_text()

#merge into one text chunk
paste(unlist(vehicle_description_text), collapse =" ")
```


Number of videos
```{r}
video_count <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]')%>%
  html_nodes(xpath='div/div[@class="post-excerpt"]//p/iframe[@src]')%>%
  length()
#  html_nodes(xpath='@src')%>%
#  html_text()#%>%
#  str_detect("youtube.com")
#  html_children()%>%html_attrs()

video_count
```

Listing Nicknames

```{r}
listing_nicknames <- 
  content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]//div//div[@class="listing-nicknames"]')%>%#[@data-gallery-items]
#  html_children()
  html_text()#%>%
#  str_remove("Filed under: ")
listing_nicknames
```

Number of photos

```{r}
photos <- content(request)%>%
  #navigate to the photo gallery node
  html_nodes(xpath='//div[@class="column column-left"]//div[@data-gallery-limit]')%>%
  #access the contents of the attribute @data-gallery-items
  html_attr('data-gallery-items')%>%
  #remove backslashes that are escape characters
  str_replace("\\\\","")%>%
  #remove the rest of the escape characters
  str_replace_all("\\\\","")%>%
  #enter the object and collapse the JSON array into index-value pairs at this level
  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
  spread_all()%>%
  as.tbl_json()

photo_count <- n_distinct(photos$id)
```

#AUCTION RESULTS

```{r}
request1<- GET("https://bringatrailer.com/listing/2006-ford-gt-33/")

request2<- GET("https://bringatrailer.com/listing/1960-land-rover-88-series-ii-4x4-6/")

request3<- GET("https://bringatrailer.com/listing/2001-acura-integra-gs-r-7/")

request4<- GET("https://bringatrailer.com/listing/2004-porsche-911-gt3-rs/")
```
```{r}
http_type(request4)
```


Auction Outcome
```{r}
auction_outcome <- content(request)%>%
  html_nodes(xpath='//div[@class="listing-available-info"]//span[@class="data-label" and position()=1]')%>%
  html_text()%>%
  tolower()%>%
  switch("sold for" = "sold"
       , "bid to" = "reserve not met"
       , "withdrawn on" = "withdrawn"
       , "current bid:" = "ongoing"
       )

auction_outcome
```
Whether Auction is Live or Not
```{r}
auction_live <- content(request)%>%
  html_nodes(xpath='//div[@class="listing-available-info"]//span[@class="data-label" and position()=1]')%>%
  html_text()%>%
  tolower()%>%
  str_detect("current bid:")

auction_live
```

Final Bid Type- winning bid or high bid
```{r}
final_bid_type <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]/tbody//tr[position()=1]//td[@class="listing-stats-label"]')%>%
  html_text()%>%
  tolower()%>%
  str_remove(" bid")

final_bid_type
```


Final Bid Amount(USD)
```{r}
final_bid_amount <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <span> tag that does NOT have the high bidder link attribute
  html_nodes(xpath='span[not(@data-listing-high-bidder-link)]')%>%
  html_text()%>%
  parse_number()


final_bid_amount

```


Winning Bidder Username
```{r}
winner_username <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <a> tag that contains the relevant text
  html_nodes(xpath='span[@data-listing-high-bidder-link]/a')%>%
  html_text()

winner_username
```

Winning Bidder Profile Link
```{r}
winner_profile <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <a> tag that contains the url
  html_nodes(xpath='span[@data-listing-high-bidder-link]/a')%>%
  #extract url as text
  html_nodes(xpath='@href')%>%
  html_text()

winner_profile
```
Date & Time of Auction End
**TIMEZONE LABEL "PT" IS UNSTABLE
```{r}
auction_ended <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[@class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[@class="listing-stats-value"]//span[@data-ends]')%>%
  html_text()%>%
  str_remove_all("at")%>%
#  str_replace("PT","US/Pacific")%>%
  parse_datetime("%B %d, %Y %H:%M %p %Z")

auction_ended
```

Total Bids in Auction

```{r}
auction_bids <- content(request1)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #tables rows that contain the specified class
  html_nodes(xpath='//tbody//tr[@class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[@class="listing-stats-value number-bids-value"]')%>%
  html_text()%>%
  as.numeric()

#if(length(auction_bids)==0)
#{
#  auction_bids<- auction_bids%>%is_null()
#  }

auction_bids
```
Total Views of Auction
```{r}
auction_views <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@id="listing-actions-stats"]')%>%
  #tables rows that contain the specified attribute
  html_nodes(xpath='tbody//tr//td//span[@data-stats-item="views"]')%>%
  html_text()%>%
  #parse for only digits
  parse_number()

auction_views
```

Total Comments
```{r}
auction_comments <- 
  content(request1)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div//h2[@class="comments-title"]')%>%
  #tables rows that contain the specified attribute
  html_text()%>%
  #parse for only digits
  parse_number()

auction_comments
```

Number of Users Watching Auction

```{r}
auction_watchers <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@id="listing-actions-stats"]')%>%
  #tables rows that contain the specified attribute
  html_nodes(xpath='tbody//tr//td//span[@data-stats-item="watchers"]')%>%
  html_text()%>%
  #parse for only digits
  parse_number()

auction_watchers
```
#AUCTION COMMENT & BID HISTORY


```{r}
#history <-
#content(request)%>%
#  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')%>%
#  html_text()

```


```{r}
guts <- content(request2)%>%
  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')

guts<- guts%>%xml_contents()%>%
  xml_text()#%>%
 # str_replace("\\\\","")%>%
  #remove the rest of the escape characters
 # str_replace_all("\\\\","")%>%
 # str_replace_all("\\\\","")
  #enter the object and collapse the JSON array into index-value pairs at this level
#  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
#  spread_all()%>%
 # as.tbl_json()

```

```{r}
guts2 <- guts%>%xml_contents()%>%
  xml_text()%>%
  str_remove_all("\\\\")%>%
  #remove the rest of the escape characters
 # str_replace_all("\\\\","")#%>%
 # str_replace_all("\\\\","")
  json_structure()
  #enter the object and collapse the JSON array into index-value pairs at this level
#  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
#  spread_all()%>%
 # as.tbl_json()

guts2
```
```{r}
x<-guts%>%
  str_remove("var BAT_VMS =")%>%
  str_remove_all("\\\\")%>%
  writeLines()

typeof(x)
length(x)
attributes(x)
x%>%json_schema()
```

Assess the JSON schema - quite a few top-level objects
```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
#  str_remove_all("\\\\","")%>%
#  str_remove_all("<")%>%
#  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_schema()
```
Take a look at the JSON structure
```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
#  str_remove_all("\\\\")%>%
#  str_remove_all("<")%>%
#  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_structure()
  
```

How complex is this JSON?
identify the complexity of deeply nested documents. The json_complexity function adds a column (default name "complexity") that contains the 'complexity' of the JSON associated with each row. 
```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
#  str_remove_all("\\\\","")%>%
#  str_remove_all("<")%>%
#  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_complexity()
```

```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
#  str_remove_all("\\\\","")%>%
#  str_remove_all("<")%>%
#  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_lengths()
```
```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
#  str_remove_all("\\\\","")%>%
#  str_remove_all("<")%>%
#  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_types()
```

```{r}
guts%>%
  str_remove("var BAT_VMS =")%>%
  str_remove_all("\\\\")%>%
  str_remove_all("<")%>%
  str_remove_all(">")%>%
  str_remove_all(";")%>%
#  enter_object()%>%
  gather_array("level.3")%>%
  #spread all scalar elements into new columns
  spread_all()%>%
  as.tbl_json()
```


```{r}

guts2 <- content(request2)%>%
  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')

guts2%>%xml_contents()%>%
  xml_text()%>%
  str_replace("var BAT_VMS =","")%>%
#  str_remove_all("\\\\")%>%
  str_remove_all("<")%>%
  str_remove_all(">")%>%
  str_remove_all(";")%>%
#  gather_array("level.3")%>%
  enter_object(channels)%>%
  spread_all()#%>%

#  json_structure()%>%
#  json_types()
  #gather_array("level.3")%>%
  #spread all scalar elements into new columns
  
 # as.tbl_json()
```



```{r}

guts2 <- content(request2)%>%
  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')

guts2%>%xml_contents()%>%
  xml_text()%>%
  str_remove("var BAT_VMS =")#%>%
#  str_replace("\\\\","")%>%
  #remove the rest of the escape characters
#  str_replace_all("\\\\","")%>%
  #enter the object and collapse the JSON array into index-value pairs at this level
#  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
#  spread_all()%>%
#  as.tbl_json()

```

```{r}
guts <- content(request)%>%
   html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')
```
```{r}
guts<- guts%>%xml_contents()%>%
   xml_text()
```
```{r}
guts%>%
   str_replace("var BAT_VMS =","")%>%
 #  str_replace_all("\\\\","")%>%
   str_remove_all("<")%>%
   str_remove_all(">")%>%
   str_remove_all(";")%>%
   json_schema()
```
```{r}
guts%>%
   str_replace("var BAT_VMS =","")%>%
 #  str_replace_all("\\\\","")%>%
   str_remove_all("<")%>%
   str_remove_all(">")%>%
   str_remove_all(";")%>%
   json_structure()
```

```{r}
y<- guts%>%
   str_replace("var BAT_VMS =","")%>%
   str_replace_all("\\\\","")%>%
#  str_remove_all("<")%>%
#   str_remove_all(">")%>%
#   str_remove_all(";")%>%
#  writeLines()#%>%
  writeChar()
#  gather_object()%>%
#  enter_object()%>%
#  gather_array(name.channels)%>%
#  spread_values()%>%
#  as.tbl_json()
  
```


```{r}
y
```

```{r}
jsonedit()
```









