---
title: "ce_scraping_rmd_to_database"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(plotly)
library(ggplot2)
library(httr)
library(stringr)
library(rvest)
library(xml2)  #XML package no longer maintained. xml2 is a newer wrapper
library(XML)
#library(R.utils)
library(tidyjson)
library(reticulate)
library(jsonlite)
```

# Obtain a list of file names from the .rds files
```{r}
file_list <- list.files(path = "../data/bat_page_responses/group_a/", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = TRUE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
```
```{r}

file_list%>%
  str_remove_all(".rds")%>%
  str_replace_all("(rows_\\d+_\\d+/)","")
```

```{r}
sample_files <- (file_list#%>%
#                   str_remove_all(".rds")%>%
#                   str_replace_all("(rows_\\d+_\\d+/)","")
                 )%>%
  sample(10)
```
```{r}
sample_files#[1]
```
#LISTING ESSENTIALS
```{r}
request <- read_rds("../data/bat_page_responses/group_a/"%>%
                      paste0(sample_files[1]))

request%>%attributes()
```
```{r}
content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_children()
```
Lot Number
```{r}
lot_number <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=1]')%>%
  html_text()%>%
  str_extract("\\d+")
lot_number
```
Seller Name
```{r}
seller_name <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=2]')%>%
  html_text()%>%
  str_remove("Seller: ")
seller_name
```

Seller Profile Link
```{r}
seller_profile <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=2]//a')%>%
  html_node(xpath='@href')%>%
  html_text()

seller_profile
```

Location Name
```{r}
location<- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=3]')%>%
  html_text()%>%
  str_remove("Location: ")

location
```

Location Google Maps Link
```{r}
location_google_maps <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=3]//a')%>%
  html_node(xpath='@href')%>%
  html_text()

location_google_maps
```

Chassis Number
```{r}
chassis <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=4]')%>%
  html_text()%>%
  str_remove("Chassis: ")

chassis
```

Odometer
```{r}
odometer <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=5]')%>%
  html_text()%>%
  str_remove("TMU")

odometer
```
TMU Indicated?
```{r}
tmu <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=5]')%>%
  html_text()%>%
  str_detect("TMU")

tmu
```

Engine
```{r}
engine <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=6]')%>%
  html_text()

engine
```
Transmission
```{r}
transmission <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]/li[position()=7]')%>%
  html_text()

transmission
```
Private Party or Dealer Listing?
```{r}
seller_type <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]//li[contains(text(),"Private Party Or Dealer") or contains(text(),"Private Party or Dealer")]')%>%
  html_text()%>%
  tolower()%>%
  str_remove("private party or dealer: ")

seller_type
```

Additional Dealer Charges?
```{r}
dealer_charges <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]//li[contains(text(),"Additional Charges From This Dealer: USD")]')%>%
                html_text()%>%
  parse_number()
  #str_remove("Additional Charges From This Dealer: USD ")
dealer_charges
```
Model Page
```{r}
#NEED TO IDENTIFY SYNTAX FOR SIBLING
#model_page <- 
  content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]/a')%>%
  html_nodes(xpath='@href[position()=1]')%>%
  html_text()
```

Model Tag
```{r}
model_tag <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[not(@rel)]')%>%
  html_text()%>%
  str_remove("Premium")
model_tag
```
Category Tag
```{r}
category_tag <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[@rel="category tag"]')%>%
  html_text()

category_tag
```

Premium Listing?
```{r}
#NEED TO IDENTIFY SYNTAX FOR SIBLING a//text()
premium <- content(request)%>%
  html_nodes(xpath='//ul[@class="listing-essentials-items"]')%>%
  html_nodes(xpath='li[@class="listing-essentials-item listing-essentials-item-categories"]//a[not(@rel)][last()]')%>%
  html_text()%>%
  str_detect("Premium")

premium
```

# AUCTION LISTING DETAILS
Vehicle description text
```{r}
vehicle_listing_text <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]')%>%
  html_nodes(xpath='div/div[@class="post-excerpt"]//p[text()]')%>%
  html_text()

vehicle_listing_text
```

Number of videos
```{r}
video_count <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]')%>%
  html_nodes(xpath='div/div[@class="post-excerpt"]//p/iframe[@src]')%>%
  length()
#  html_nodes(xpath='@src')%>%
#  html_text()#%>%
#  str_detect("youtube.com")
#  html_children()%>%html_attrs()

video_count
```

Listing Nicknames

```{r}
listing_nicknames <- 
  content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]//div//div[@class="listing-nicknames"]')%>%#[@data-gallery-items]
#  html_children()
  html_text()
```

Number of photos

```{r}
photos <- content(request)%>%
  #navigate to the photo gallery node
  html_nodes(xpath='//div[@class="column column-left"]//div[@data-gallery-limit]')%>%
  #access the contents of the attribute @data-gallery-items
  html_attr('data-gallery-items')%>%
  #remove backslashes that are escape characters
  str_replace("\\\\","")%>%
  #remove the rest of the escape characters
  str_replace_all("\\\\","")%>%
  #enter the object and collapse the JSON array into index-value pairs at this level
  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
  spread_all()%>%
  as.tbl_json()

photo_count <- n_distinct(photos$id)
```

#AUCTION RESULTS

```{r}
request1<- GET("https://bringatrailer.com/listing/2006-ford-gt-33/")

request2<- GET("https://bringatrailer.com/listing/1960-land-rover-88-series-ii-4x4-6/")

request3<- GET("https://bringatrailer.com/listing/2001-acura-integra-gs-r-7/")

request4<- GET("https://bringatrailer.com/listing/2004-porsche-911-gt3-rs/")
```

Auction Outcome
```{r}
auction_outcome <- content(request4)%>%
  html_nodes(xpath='//div[@class="listing-available-info"]//span[@class="data-label" and position()=1]')%>%
  html_text()%>%
  tolower()%>%
  switch("sold for" = "sold"
       , "bid to" = "reserve not met"
       , "withdrawn on" = "withdrawn"
       , "current bid:" = "ongoing"
       )

auction_outcome
```
Whether Auction is Live or Not
```{r}
auction_live <- content(request4)%>%
  html_nodes(xpath='//div[@class="listing-available-info"]//span[@class="data-label" and position()=1]')%>%
  html_text()%>%
  tolower()%>%
  str_detect("current bid:")

auction_live
```

Final Bid Type- winning bid or high bid
```{r}
final_bid_type <- content(request)%>%
  html_nodes(xpath='//div[@class="column column-left"]//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]/tbody//tr[position()=1]//td[@class="listing-stats-label"]')%>%
  html_text()%>%
  tolower()%>%
  str_remove(" bid")

final_bid_type
```


Final Bid Amount(USD)
```{r}
final_bid_amount <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <span> tag that does NOT have the high bidder link attribute
  html_nodes(xpath='span[not(@data-listing-high-bidder-link)]')%>%
  html_text()%>%
  parse_number()


final_bid_amount

```

Winning Bidder Username
```{r}
winner_username <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <a> tag that contains the relevant text
  html_nodes(xpath='span[@data-listing-high-bidder-link]/a')%>%
  html_text()

winner_username
```

Winning Bidder Profile Link
```{r}
winner_profile <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[position()=1 and @class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[position()=2 and @class="listing-stats-value"]')%>%
  #select the <a> tag that contains the url
  html_nodes(xpath='span[@data-listing-high-bidder-link]/a')%>%
  #extract url as text
  html_nodes(xpath='@href')%>%
  html_text()

winner_profile
```
Date & Time of Auction End
**TIMEZONE LABEL "PT" IS UNSTABLE
```{r}
auction_ended <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #from table body select first table row that also has the specified class
  html_nodes(xpath='//tbody//tr[@class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[@class="listing-stats-value"]//span[@data-ends]')%>%
  html_text()%>%
  str_remove_all("at")%>%
#  str_replace("PT","US/Pacific")%>%
  parse_datetime("%B %d, %Y %H:%M %p %Z")

auction_ended
```

Total Bids in Auction

```{r}
total_bids <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@class="listing-stats ended"]')%>%
  #tables rows that contain the specified class
  html_nodes(xpath='//tbody//tr[@class="listing-stats-stat"]')%>%
  #from this row, select second table data item with the specified class
  html_nodes(xpath='td[@class="listing-stats-value number-bids-value"]')%>%
  html_text()

total_bids
```
Total Views of Auction
```{r}
views <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@id="listing-actions-stats"]')%>%
  #tables rows that contain the specified attribute
  html_nodes(xpath='tbody//tr//td//span[@data-stats-item="views"]')%>%
  html_text()%>%
  #parse for only digits
  parse_number()

views
```

Total Number Views of Auction

```{r}
watchers <- content(request)%>%
  #bid container and table with auction stats
  html_nodes(xpath='//div[@id="listing-bid-container"]/table[@id="listing-actions-stats"]')%>%
  #tables rows that contain the specified attribute
  html_nodes(xpath='tbody//tr//td//span[@data-stats-item="watchers"]')%>%
  html_text()%>%
  #parse for only digits
  parse_number()

watchers
```
#AUCTION COMMENT & BID HISTORY


```{r}
#history <-
content(request)%>%
  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')%>%
  html_text()

```




```{r}
guts <- content(request)%>%
  html_nodes(xpath='//script[@id="bat-theme-viewmodels-js-extra"]')

guts<- guts%>%xml_contents()%>%
  xml_text()#%>%
 # str_replace("\\\\","")%>%
  #remove the rest of the escape characters
 # str_replace_all("\\\\","")%>%
 # str_replace_all("\\\\","")
  #enter the object and collapse the JSON array into index-value pairs at this level
#  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
#  spread_all()%>%
 # as.tbl_json()

```
```{r}
guts%>%
  str_replace("var BAT_VMS =","")%>%
#  str_replace_all("\\\\","")%>%
  str_remove_all("<")%>%
  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_schema()

guts%>%
  str_replace("var BAT_VMS =","")%>%
#  str_replace_all("\\\\","")%>%
  str_remove_all("<")%>%
  str_remove_all(">")%>%
  str_remove_all(";")%>%
  json_structure()
  
```
```{r}
guts%>%
  str_replace("var BAT_VMS =","")%>%
#  str_replace_all("\\\\","")%>%
  str_remove_all("<")%>%
  str_remove_all(">")%>%
  str_remove_all(";")%>%
  gather_array("level.3")%>%
  #spread all scalar elements into new columns
  spread_all()%>%
  as.tbl_json()
```


```{r}
guts
```



```{r}


str_replace("\\\\","")%>%
  #remove the rest of the escape characters
  str_replace_all("\\\\","")%>%
  #enter the object and collapse the JSON array into index-value pairs at this level
  gather_array("levels.2")%>%
  #spread all scalar elements into new columns
  spread_all()%>%
  as.tbl_json()
guts%>%
  xml_contents()%>%
  xml_text()%>%
  parse_character()
```



